A preliminary constraint grammar for Russian

### 2015-05-04 2015-nodalida-ruscg/ruscg.tex
some finishing touches
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60242 72bbbca6-d526-0410-a7d9-f06f51895060

\begin{figure*}
\centering
\begin{multicols}{2}
\begin{alltt}
{\small

@@

@@

\begin{table}
  \centering
  \begin{tabular}{|l|r|r|}

    \hline
    Error in original        &   & 2  \\
    Missing lexeme           &   & 8  \\   % безбалластный, FALSENEG: Кий<np><ant><m><sg><ins> ['кий<n><m><nn><sg><ins>']
    Partial lexeme           &   & 2  \\   % франко-норманнское, рельс
    Missing analysis         &   &    \\   % 
    Equally valid analysis   &   &    \\   % большой<adj><comp><pred> ['больше<adv>'] (?)
    Correct reading removed  &   & 34 \\   % 
    \hline
                             &   & 46 \\
    \hline
  \end{tabular}
  \caption{Error analysis of false negatives}
\end{table}

@@

\subsection{Quantitative evaluation}
% ROB accent placement task

@@

\rr{Emphasize R2's thoughts more in conclusion: I particularly like the idea of systematically assigning rules to heuristicity sections based on performance thresholds derived from annotation-inspection of a non-gold corpus. Another novel idea (at least in terms of actual implementation) is to go for 100\% recall and add a hybridized HMM-tagger in order to improve precision.}

@@

We are grateful to Koen Claessen for insightful discussion, as well as three anonymous reviewers who 
gave thoughtful feedback on an earlier version of this paper. All remaining errors are our own. 
\rr{Revise acknowledgments!}

>>>>

\begin{figure*}
\centering
\begin{multicols}{2}
\noindent
\begin{alltt}
{\small

@@

Table~\ref{table:results} gives a quantitative evaluation of the performance of our CG on the test corpus.

@@

%\begin{table}
%  \centering
%  \begin{tabular}{|l|r|r|}
%    
%    \hline
%    Error in original        &   & 2  \\
%    Missing lexeme           &   & 8  \\   % безбалластный, FALSENEG: Кий<np><ant><m><sg><ins> ['кий<n><m><nn><sg><ins>']
%    Partial lexeme           &   & 2  \\   % франко-норманнское, рельс
%    Missing analysis         &   &    \\   % 
%    Equally valid analysis   &   &    \\   % большой<adj><comp><pred> ['больше<adv>'] (?)
%    Correct reading removed  &   & 34 \\   % 
%    \hline
%                             &   & 46 \\
%    \hline
%  \end{tabular}
%  \caption{Error analysis of false negatives}
%\end{table}

@@

\subsection{Task-based evaluation}
% ROB accent placement task

@@

@@

We are grateful to Koen Claessen for insightful discussion, as well as three anonymous reviewers who 
gave thoughtful feedback on an earlier version of this paper. All remaining errors are our own.
